---
title: "Task 3 - Seabirds"
output:
  html_document:
    df_print: paged
---

# Introduction

This task included four sheets in the xls file `seabirds.xls` that report on birds that are spotted on ships.

The dataset that I created was built to serve the purpose of answering these questions. Much of the data from the seabird.xls was fairly unnecessary for the purposes of answering these questions. 

Some of the assumptions I made in cleaning the data, was that any bird_count that has the value of NA should be removed, since it is hard to argue what that value should be. If I were able to talk to those who collected the data it would have been easier whether or not to allocate a value to the NA's.

Two "code" sheets also accompanied the main two "record" sheets. For the most part these two code sheets provided that wasnt of much use, however it was useful in indicating which data has essentially been duplicated across columns in the record sheets. 


### Package loadin
```{r}
library(tidyverse)
library(stringr)
library(dplyr)
library(tidyr)
```

### Reading in the clean data from csv created by the cleaning script
```{r}
bird_ship <- read_csv("~/dirty_data_project/task_03/clean_data/clean_bird_ship.csv")
```

### Verifying the data 
```{r}
str(bird_ship)
```

# 1.3.2 Analysis questions

1. Which bird had the most individual sightings?
```{r}
bird_ship %>%
  group_by(species_common_name) %>%
  filter(bird_count == 1) %>%
  summarise(total_count = sum(bird_count)) %>%
  slice_max(total_count, n = 1)

```

2. Which bird had the highest total count?
```{r}
bird_ship %>%
  group_by(species_common_name) %>%
  drop_na(bird_count) %>%
  summarise(total_count = sum(bird_count)) %>%
  slice_max(total_count)

```

3. Which bird had the highest total count above a latitude of -30?
```{r}
bird_ship %>%
  filter(latitude > -30) %>%
  group_by(species_common_name) %>%
  summarise(total_count = sum(bird_count)) %>%
  slice_max(total_count)

```


4. How many different types of birds were only ever seen in groups of 1?
```{r}
bird_ship %>% 
    filter(bird_count < 2)  %>% 
        select(species_common_name, species_scientific_name, species_abbreviation) %>%
        distinct() %>% 
    arrange(species_abbreviation) %>% 
    count()
```


5. How many penguins were seen? (Hint: there are many types of penguin)
```{r}
bird_ship %>% 
  filter(str_detect(species_common_name, "[Pp]enguin")) %>%
  summarise(total_count = sum(bird_count))
```

