---
title: "Task 2 - Analysis and Documentation"
output: html_document
---

loading in packages and data

```{r, warning=FALSE, results=FALSE}
library(tidyverse)
library(here)
```

```{r, echo=T, results=FALSE, warning=FALSE, error=FALSE, message=FALSE}
cake <- read_csv(here("clean_data/cake.csv"))
```

### Question 1 
Which cake has the most cocoa in it?
```{r}
cake %>%
  filter(ingredient == "Cocoa") %>%
  arrange(desc(ingredient)) %>%
  slice_max(1)
```

### Question 2
For sponge cake, how many cups of ingredients are used in total?
```{r}
cake %>%
  filter(cake == "Sponge") %>%
  filter(measure == "cup") %>%
  nrow()
```

### Question 3 
How many ingredients are measured in teaspoons?
```{r}
cake %>%
  filter(measure == "teaspoon") %>%
  summarise(ingre_teaspoon = n_distinct(ingredient))
```

### Question 4 
Which cake has the most unique ingredients?
```{r}
cake %>%
  group_by(cake) %>%
  summarise(num_of_ingredients = n()) %>%
  arrange(desc(num_of_ingredients)) %>%
  slice_head(n = 2)
```

### Question 5 
Which ingredients are used only once?
```{r}
cake %>%
  group_by(ingredient) %>%
  summarise(num_cake = n()) %>%
  filter(num_cake == 1)
```

### Question 6 (my own question)
Average number of ingredients in a cake
```{r}
cake %>%
  group_by(cake) %>%
  summarise(num_ingredients = n()) %>%
  summarise(avg_ingr = mean(num_ingredients))
```


