---
title: "Task 1 - Analysis and Documentation"
output: html_document
---

loading in packages and data

```{r, warning=FALSE, results=FALSE}
library(tidyverse)
library(here)
```

```{r, echo=T, results=FALSE, warning=FALSE, error=FALSE, message=FALSE}
decathalon <- read_csv(here("clean_data/clean_decathlon_ds.csv"))
```

### Question 1 
Who had the longest long jump seen in the data?
```{r}
decathalon %>%
  filter(event == "long_jump") %>%
  arrange(desc(score)) %>%
  slice_max(1)
```

### Question 2
What was the average 100m time in each competition?
```{r}
decathalon %>%
  filter(event == "one_hundred_meters") %>%
  group_by(competition) %>%
  summarise(average_time = mean(score))
```

### Question 3
Who had the highest total points across both competitions?
```{r}
decathalon %>%
  distinct(surname, competition, points) %>%
  group_by(surname) %>%
  summarise(total_points = sum(points)) %>%
  arrange(desc(total_points)) %>%
  slice_max(1)
```

### Question 4
What was the shot-put scores for the top three competitors in each competition?
```{r}
decathalon %>%
  filter(event == "shot_put") %>%
  filter(rank < 4) 
```

### Question 5
What was the average points for competitors who ran the 400m in less than 50 seconds vs. those than ran 400m in more than 50 seconds?
```{r}
decathalon %>%
  filter(event == "four_hundred_meters") %>%
  mutate(fast_400 = score < 50) %>%
  group_by(fast_400) %>%
  summarise(average_points = mean(points)) 
  
```



