---
title: "Test Zone"
output: html_notebook
---

bird_data_record <- read_excel("~/dirty_data_project/task_03/data/seabirds.xls", sheet = 2)
ship_data_codes <- read_excel("~/dirty_data_project/task_03/data/seabirds.xls", sheet = 3)
bird_data_codes <- read_excel("~/dirty_data_project/task_03/data/seabirds.xls", sheet = 4)

```{r}
library(tidyverse)
library(stringr)
```


```{r}
ship_data_record %>%
  select(-c(SACT:LONGECELL))
```

```{r}
test <- ship_data_record %>%
  select(-c(SACT:LONGECELL)
  ) %>%
  rename(
    id = "RECORD",
    record_id = "RECORD ID",
    date = "DATE",
    time = "TIME",
    latitude = "LAT",
    longitude = "LONG",
    east_or_west_hemisphere = "EW",
  ) %>%
  mutate(
    time = str_remove(time, "1899-12-31"),
    time = str_remove(time, "1900-01-01"),
    east_or_west_hemisphere = str_replace(east_or_west_hemisphere, "E", "Eastern Hemisphere"),
    east_or_west_hemisphere = str_replace(east_or_west_hemisphere, "W", "Western Hemisphere")
  ) %>%
  drop_na()

test
```

```{r}

test_birds <- bird_data_record %>%
  select(RECORD, 
         `RECORD ID`, 
         `Species common name (taxon [AGE / SEX / PLUMAGE PHASE])`, 
         `Species  scientific name (taxon [AGE /SEX /  PLUMAGE PHASE])`, 
         `Species abbreviation`, 
         COUNT
  ) %>%
  rename(
    record = "RECORD",
    record_id = "RECORD ID",
    species_common_name = "Species common name (taxon [AGE / SEX / PLUMAGE PHASE])",
    species_scientific_name = "Species  scientific name (taxon [AGE /SEX /  PLUMAGE PHASE])",
    species_abbreviation = "Species abbreviation",
    count = "COUNT"
  ) %>%
  mutate(
    species_common_name = str_remove_all(species_common_name, "SUBAD"),
    species_common_name = str_remove_all(species_common_name, "IMM"),
    species_common_name = str_remove_all(species_common_name, "AD"),
    species_common_name = str_remove_all(species_common_name, "JUV"),
    species_common_name = str_remove_all(species_common_name, "PL1"),
    species_common_name = str_remove_all(species_common_name, "PL2"),
    species_common_name = str_remove_all(species_common_name, "PL3"),
    species_common_name = str_remove_all(species_common_name, "PL4"),
    species_common_name = str_remove_all(species_common_name, "PL5"),
    species_common_name = na_if(species_common_name, "[NO BIRDS RECORDED]")
    species_common_name = str_remove_all(species_common_name, "SUBAD"),
    species_common_name = str_remove_all(species_common_name, "IMM"),
    species_common_name = str_remove_all(species_common_name, "AD"),
    species_common_name = str_remove_all(species_common_name, "JUV"),
    species_common_name = str_remove_all(species_common_name, "PL1"),
    species_common_name = str_remove_all(species_common_name, "PL2"),
    species_common_name = str_remove_all(species_common_name, "PL3"),
    species_common_name = str_remove_all(species_common_name, "PL4"),
    species_common_name = str_remove_all(species_common_name, "PL5"),

  ) %>%
  drop_na(species_common_name)

test_birds
```



