---
title: "Analysis"
output: html_notebook
---

```{r}
library(tidyverse)
library(stringr)
library(readr)
```

```{r}
clean_candy <- read_csv("../clean_data/clean_candy.csv", col_types = cols(country = col_character(), gender = col_character()))
```

```{r}
clean_candy
```


# 1.4.2 Analysis questions

1. What is the total number of candy ratings given across the three years. (number of candy ratings, not number of raters. Don’t count missing values)

```{r}
clean_candy %>%
  select(rating) %>%
  summarise(n = n()
)
```


2. What was the average age of people who are going out trick or treating and the average age of people 3. not going trick or treating?


```{r}
clean_candy %>%
  filter(going_trick_or_treating == "Yes") %>%
  summarise(average_age = mean(age))

clean_candy %>%
  filter(going_trick_or_treating == "No") %>%
  summarise(average_age = mean(age))
```


3. For each of joy, despair and meh, which candy bar revived the most of these ratings?

```{r}
clean_candy %>%
  filter(rating == "DESPAIR") %>%
  group_by(candy) %>%
  summarise(n = n()) %>%
  slice_max(n, n = 1)
```


4. How many people rated Starburst as despair?

```{r}
clean_candy %>%
  filter(candy == "starburst",
         rating == "DESPAIR") %>%
  summarise(n = n())
```


6. What was the most popular candy bar by this rating system for each gender in the dataset?

```{r}
clean_candy %>%
  filter(rating == "JOY",
         gender == "Female") %>%
  group_by(candy)
  
```

7. What was the most popular candy bar in each year?

```{r}
clean_candy %>%
  group_by(year) 
```


8. What was the most popular candy bar by this rating for people in US, Canada, UK and all other countries?

```{r}

```


