---
title: "Analysis"
output: html_notebook
---

```{r}
library(tidyverse)
library(stringr)
library(readr)
library(dplyr)
library(tidyr)
```

```{r}
clean_candy <- read_csv("../clean_data/clean_candy.csv", col_types = cols(country = col_character(), gender = col_character()))
```

```{r}
clean_candy
```


# 1.4.2 Analysis questions

1. What is the total number of candy ratings given across the three years. (number of candy ratings, not number of raters. Don’t count missing values)

```{r}
clean_candy %>%
  select(candy) %>%
  summarise(n = n()
)
```


2. What was the average age of people who are going out trick or treating and the average age of people 3. not going trick or treating?


```{r}
clean_candy %>%
  group_by(going_trick_or_treating) %>%
  summarise(average_age = mean(age))

```


3. For each of joy, despair and meh, which candy bar revived the most of these ratings?

```{r}
clean_candy %>%
  group_by(rating, candy) %>%
  summarise(n = n()) %>%
  slice_max(n)

```


4. How many people rated Starburst as despair?

```{r}
clean_candy %>%
  filter(candy == "starburst",
         rating == "DESPAIR") %>%
  summarise(n = n())
```

# Mutating despair, joy, and meh to -1, 1, and 0

```{r}
mutated_clean_candy <- clean_candy %>%
  mutate(rating_count = recode(rating,
                         DESPAIR = -1,
                         MEH = 0,
                         JOY = 1
                         ))
mutated_clean_candy
```
clean_full_candy$age <- as.integer(as.character(clean_full_candy$age))

6. What was the most popular candy bar by this rating system for each gender in the dataset?

```{r}
mutated_clean_candy %>%
  group_by(gender, candy) %>%
  summarise(total_preference = sum(rating_count)) %>%
  filter(candy != "any_full_sized_candy_bar") %>%
  slice_max(total_preference)
```

7. What was the most popular candy bar in each year?

```{r}
mutated_clean_candy %>%
  group_by(year, candy) %>%
  summarise(total_preference = sum(rating_count)) %>%
  filter(candy != "any_full_sized_candy_bar") %>%
  slice_max(total_preference)
```


8. What was the most popular candy bar by this rating for people in US, Canada, UK and all other countries?

```{r}
mutated_clean_candy %>%
  mutate(country = if_else(country %in% c("USA", "Canada", "United Kingdom"), country, "other")) %>%
  filter(year != 2015) %>%
  group_by(country, candy) %>%
  summarise(total_preference = sum(rating_count)) %>%
  filter(candy != "any_full_sized_candy_bar") %>%
  slice_max(total_preference)
```


